---
title: ""
author: Matt and Jordan
date: ""
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

```{r packages}
# Load packages
```

## Study Information

### 1.	Title 

Quantification of aggressive behavior in Drosophila melanogaster

### 2.	Authorship

Matt and Jordan

^1^ Affiliation A

### 3.	Research Questions 

Do flies that are bred for aggressive tendacies have a higher number of escalations than flies bred for neutral tendacies?

### 4.	Hypotheses

1. Yes, aggressive flies at generation 11 will show a significant difference in escalations than neutra flies.
 
## Sampling Plan

In this section we will ask you to describe how you plan to collect samples, as well as the number of samples you plan to collect and your rationale for this decision. Please keep in mind that the data described in this section should be the actual data used for analysis, so if you are using a subset of a larger dataset, please describe the subset that will actually be used in your study.

Look at aggressive and non aggressive flies, choose flies based on their behavior, and then randomly put them in groups, record aggressive tendancies via video recording.

### 5.	Existing data

*5.1.	Preregistration is designed to make clear the distinction between confirmatory tests, specified prior to seeing the data, and exploratory analyses conducted after observing the data. Therefore, creating a research plan in which existing data will be used presents unique challenges. Please select the description that best describes your situation. Please do not hesitate to contact us if you have questions about how to answer this question (prereg@cos.io).*

No existing data

### 6.	Explanation of existing data

No existing data

### 7.	Data collection procedures.

*7.1.	Please describe the process by which you will collect your data. If you are using human subjects, this should include the population from which you obtain subjects, recruitment efforts, payment for participation, how subjects will be selected for eligibility from the initial pool (e.g. inclusion and exclusion rules), and your study timeline. For studies that don’t include human subjects, include information about how you will collect samples, duration of data gathering efforts, source or location of samples, or batch numbers you will use.* 

Have 3 groups: neutral only, aggressive only, and mixed. In mixed, record instance of aggressive behavior and record type of fly that had that behavior via high speed video recording.

### 8.	Sample size

*8.1.	Describe the sample size of your study. How many units will be analyzed in the study? This could be the number of people, birds, classrooms, plots, interactions, or countries included. If the units are not individuals, then describe the size requirements for each unit. If you are using a clustered or multilevel design, how many units are you collecting at each level of the analysis?*

N = 60 in each group


### 9.	Sample size rationale

*9.1.	This could include a power analysis or an arbitrary constraint such as time, money, or personnel.*

Following the Dierick model/paper

### 10.	Stopping rule

*10.1.	If your data collection procedures do not give you full control over your exact sample size, specify how you will decide when to terminate your data collection.* 

This is not necessary

## Variables

In this section you can describe all variables (both manipulated and measured variables) that will later be used in your confirmatory analysis plan. In your analysis plan, you will have the opportunity to describe how each variable will be used. If you have variables that you are measuring for exploratory analyses, you are not required to list them, though you are permitted to do so.

### 11.	Manipulated variables

*11.1.	Describe all variables you plan to manipulate and the levels or treatment arms of each variable. For observational studies and meta-analyses, simply state that this is not applicable.*

Not applicable

### 12.	Measured variables

*12.1.	Describe each variable that you will measure. This will include outcome measures, as well as any predictors or covariates that you will measure. You do not need to include any variables that you plan on collecting if they are not going to be included in the confirmatory analyses of this study.*

Measuring instances of escalations


### 13.	Indices

*13.1.	If any measurements are going to be combined into an index (or even a mean), what measures will you use and how will they be combined? Include either a formula or a precise description of your method. If you are using a more complicated statistical method to combine measures (e.g. a factor analysis), you can note that here but describe the exact method in the analysis plan section.*


Use a behavior indice

"In these encounters, a territory holder is challenged by an intruder, and both males reciprocally box and tussle while standing on their hind legs in an attempt to maintain or take over sole territorial control"

## Design Plan


Essentially placed the flies in a cage together, (unsure whether there would be food present or not), record flies for 6 hours, 12pm to 6pm, take average of escalations per hour.

### 14.	Study type

Experiment and observational


### 15.	Blinding


-	No blinding is involved in this study.


### 16.	Study design

*16.1.	Describe your study design. Examples include two-group, factorial, randomized block, and repeated measures. Is it a between (unpaired), within-subject (paired), or mixed design? Describe any counterbalancing required. Typical study designs for observation studies include cohort, cross sectional, and case-control studies.*

Just two group? 

### 17.	Randomization

*17.1.	If you are doing a randomized study, how will you randomize, and at what level?*

This isn't randomized

## Analysis Plan

You may describe one or more confirmatory analysis in this preregistration. Please remember that all analyses specified below must be reported in the final article, and any additional analyses must be noted as exploratory or hypothesis generating.

A confirmatory analysis plan must state up front which variables are predictors (independent) and which are the outcomes (dependent), otherwise it is an exploratory analysis. You are allowed to describe any exploratory work here, but a clear confirmatory analysis is required. 

Two sample t test?

Kruskal-Wallace
Wilxcocin 


### 18.	Statistical models

*18.1.	What statistical model will you use to test each hypothesis? Please include the type of model (e.g. ANOVA, multiple regression, SEM, etc) and the specification of the model (this includes each variable that will be included as predictors, outcomes, or covariates). Please specify any interactions that will be tested and remember that any test not included here must be noted as an exploratory test in your final article.*

Two sample t test?

### 19.	Transformations

*19.1.	If you plan on transforming, centering, recoding the data, or will require a coding scheme for categorical variables, please describe that process.*

No?

### 20.	Follow-up analyses

*20.1.	If not specified previously, will you be conducting any confirmatory analyses to follow up on effects in your statistical model, such as subgroup analyses, pairwise or complex contrasts, or follow-up tests from interactions. Remember that any analyses not specified in this research plan must be noted as exploratory.*

No?

### 21.	Inference criteria

*21.1.	What criteria will you use to make inferences? Please describe the information you will use (e.g. p-values, Bayes factors, specific model fit indices), as well as cut-off criterion, where appropriate. Will you be using one or two tailed tests for each of your analyses? If you are comparing multiple conditions or testing multiple hypotheses, will you account for this?*

P value < 0.001

### 22.	Data exclusion

*22.1.	How will you determine what data or samples, if any, to exclude from your analyses? How will outliers be handled?*

N/A  

### 23.	Missing data

*23.1.	How will you deal with incomplete or missing data?*

Not paired so we can exclude N/As

### 24.	Exploratory analysis (optional)

*24.1.	If you plan to explore your data set to look for unexpected differences or relationships, you may describe those tests here. An exploratory test is any test where a prediction is not made up front, or there are multiple possible tests that you are going to use. A statistically significant finding in an exploratory test is a great way to form a new confirmatory hypothesis, which could be registered at a later time.* 

N/A

## Script (Optional) 

The purpose of a fully commented analysis script is to unambiguously provide the responses to all of the questions raised in the analysis section. This step is not common, but we encourage you to try to create an analysis script, refine it using a modeled dataset, and use it in place of your written analysis plan.

N/A

### 25.	Analysis scripts (Optional)

*25.1.	(Optional) Upload an analysis script with clear comments. This optional step is helpful in order to create a process that is completely transparent and increase the likelihood that your analysis can be replicated. We recommend that you run the code on a simulated dataset in order to check that it will run without errors.*

 N/A

## Other

### 26.	Other

*26.1.	If there is any additional information that you feel needs to be included in your preregistration, please enter it here.*

N/A

## References 

Dierick, H. & Greenspan, R. "Molecular analysis of flies selected for aggressive behavior". 2006. Nature Genetics. 38(9):1023-1031.